The effect of linking assumptions and number of response options on inferred scalar implicature rate

### 2018-05-02 writeup.Rmd
added all confidence intervals and editted some more

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
theme_set(theme_bw(18))
```

@@

```{r linkvisualization, fig.env = "figure", fig.align='center', fig.width=5, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
grid::grid.raster(link_img)
```

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1

implicature_rate <- 
  pragmatic_trials %>% gather("definition","implicature", high:low)

@@

```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=2, fig.height=1.5, set.cap.width=T, num.cols.cap=1, fig.width=1.5,fig.cap = "Cards used in the connective guessing game."}
cards_img <- jpeg::readJPEG("experiments/figs/cards.jpg")
grid::grid.raster(cards_img)
```

@@

Participants could derive implicatures in two trial types. First, the trial type in which two animals were present on the card (e.g. cat and dog) but Bob guessed only one of them (e.g. "there is a cat"). Such trials can have a literal interpretation (cat and possibly more) or an exhaustive interpretation (only cat). We refer to them as "exhaustive". The second trial type with implicatures was the one in which two animals were on the card (e.g. cat and dog) and Bob used a disjunciton (e.g. cat or dog). These trials can have a literal (inclusive) interpretation (e.g. cat or dog or both), or an exclusive interpretation (e.g. cat or dog, not both). We refer to these trials as "scalar". The following four trial types were used as experimental control: two trial types where there was no overlap between the guess (e.g. elephant) and the animal(s) on the card (e.g. cat, cat and dog); and two trial types where the animal(s) on the card were correctly guessed. For example, if there was only a cat on the card, Bob said "there is a cat" and if there was a cat and a dog, Bob said "there is a cat and a dog".

@@

```{r trials, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.width=1.5, fig.cap = "Trial types represented by example cards and guesses."}
trials_img <- jpeg::readJPEG("experiments/figs/trialTypes.jpg")
grid::grid.raster(trials_img)
```

@@

```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}

binary_summary<-
  data %>%
  filter(response_type=="binary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

binary_summary$response <- factor(binary_summary$response, levels = c("Wrong","Right"))
binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

@@

```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}

ternary_summary<-
  data %>%
  filter(response_type=="ternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

ternary_summary$response <- factor(ternary_summary$response, levels = c("Wrong","Neither", "Right"))
ternary_summary$guess_type <- factor(ternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
ternary_summary$guess_type <- recode(ternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

ternary_plot<-
  ternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=15)) +
  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)

@@

```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}

quaternary_summary<-
  data %>%
  filter(response_type=="quaternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

quaternary_summary$response <- factor(quaternary_summary$response, levels = c("Wrong","Kinda Wrong", "Kinda Right", "Right"))
quaternary_summary$guess_type <- factor(quaternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quaternary_summary$guess_type <- recode(quaternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

quaternary_plot<-
  quaternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)

@@

```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}

quinary_summary<-
  data %>%
  filter(response_type=="quinary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

quinary_summary$response <- factor(quinary_summary$response, levels = c("Wrong","Kinda Wrong", "Neither", "Kinda Right", "Right"))
quinary_summary$guess_type <- factor(quinary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quinary_summary$guess_type <- recode(quinary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

quinary_plot<-
  quinary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)

@@

### Analysis

@@

This study set out to test two linking assumptions.

We test this hypothesis formally using a binomial mixed effects model with the fixed effect of response type and the random intercept for participants as well as random intercept and slope for

A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.

All the analytical decisions described here were pre-registered in an as.predicted format. You can access the preregistration

```{r implicatureResultss}
implicature_results<-
  implicature_rate %>%
  group_by(response_type, trial_type, implicature, definition) %>%
  summarize(counts = n()) %>%
  group_by(response_type, trial_type, definition) %>%
  mutate(total = sum(counts), proportion = counts/total)
```

```{r}
implicature_results$response_type <- fct_relevel(implicature_results$response_type, "binary", "ternary", "quaternary", "quinary")
implicature_results$implicature <- as.factor(implicature_results$implicature)
implicature_results$implicature <- fct_recode(implicature_results$implicature, yes = "1", no = "0")
```

```{r implicatureRatePlot}
ggplot(implicature_results, aes(x=response_type,y=proportion)) +
  geom_bar(aes(fill = implicature), stat="identity") +
  facet_grid(definition ~ trial_type, drop = TRUE) +
  theme_few() + 
  labs(x="Implicature") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r implicatureRate, echo=FALSE, eval=FALSE}
implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)

summary(implicature_analysis_a)
library(brms)
implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="bernoulli", data=implicature_rate)
```

>>>>

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
library(DescTools)
library(binom)
theme_set(theme_bw(18))
```

@@

```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
grid::grid.raster(link_img)
```

@@

# weak definition only considers the highest point on the scale as "literal"
pragmatic_trials$weak<-1
pragmatic_trials[pragmatic_trials$response=="Right",]$weak <-0

# strong definition only considers the lowest point on the scale as implicature 
pragmatic_trials$strong<-0
pragmatic_trials[pragmatic_trials$response=="Wrong",]$strong <-1

implicature_rate <- 
  pragmatic_trials %>% gather("definition","implicature", weak:strong)

@@

```{r stimuli, fig.asp=0.35, fig.cap = "Cards used in the connective guessing game."}
cards_img <- jpeg::readJPEG("experiments/figs/cards.jpg")
grid::grid.raster(cards_img)
```

@@

Participants could derive implicatures in two trial types. First, the trial type in which two animals were present on the card (e.g. cat and dog) but Bob guessed only one of them (e.g. "there is a cat"). Such trials can have a literal interpretation (cat and possibly more) or an exhaustive interpretation (only cat). We refer to them as "exhaustive". The second trial type with implicatures was the one in which two animals were on the card (e.g. cat and dog) and Bob used a disjunciton (e.g. cat or dog). These trials can have a literal (inclusive) interpretation (e.g. cat or dog or both), or an exclusive interpretation (e.g. cat or dog, not both). We refer to these trials as "scalar". The following four trial types were used as experimental control: two trial types where there was no overlap between the guess (e.g. elephant) and the animal(s) on the card (e.g. cat, cat and dog); and two trial types where the animal(s) on the card were correctly guessed. For example, if there was only a cat on the card, Bob said "there is a cat" and if there was a cat and a dog, Bob said "there is a cat and a dog". Since the fictional character was blindfolded and did not see the outcome of the game, the ignorance inference commonly associated with disjunction was already common ground in the experimental setting. If the character was seeing the cards or knew what was on them, a disjunction would have violated the expectation that the speaker does not know which alternative actually holds. Our study controls for the possibile effect of ignorance violations on exclusivity and exhaustive inferences.

@@

```{r trials, fig.asp=0.35, fig.cap = "Trial types represented by example cards and guesses."}
trials_img <- jpeg::readJPEG("experiments/figs/trialTypes.jpg")
grid::grid.raster(trials_img)
```

@@

```{r binaryData}
binary_summary<-
  data %>%
  filter(response_type=="binary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), est=count/total)

binary_summary_X_cat <-
  binary_summary %>%
  filter(card_type=="X", guess_type=="X")
binary_summary_X_cat_confint <-
  binary_summary_X_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_X_cat <- binary_summary_X_cat %>% full_join(binary_summary_X_cat_confint, by="est")

binary_summary_XY_cat <-
  binary_summary %>%
  filter(card_type=="XY", guess_type=="X")
binary_summary_XY_cat_confint <-
  binary_summary_XY_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_XY_cat <- binary_summary_XY_cat %>% full_join(binary_summary_XY_cat_confint, by="est")

binary_summary_XY_ele <-
  binary_summary %>%
  filter(card_type=="XY", guess_type=="Z")
binary_summary_XY_ele_confint <-
  binary_summary_XY_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_XY_ele <- binary_summary_XY_ele %>% full_join(binary_summary_XY_ele_confint, by="est") %>% unique()

binary_summary_X_ele <-
  binary_summary %>%
  filter(card_type=="X", guess_type=="Z")
binary_summary_X_ele_confint <-
  binary_summary_X_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_X_ele <- binary_summary_X_ele %>% full_join(binary_summary_X_ele_confint, by="est") %>% unique()

binary_summary_XY_and <-
  binary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
binary_summary_XY_and_confint <-
  binary_summary_XY_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_XY_and <- binary_summary_XY_and %>% full_join(binary_summary_XY_and_confint, by="est") %>% unique()

binary_summary_X_and <-
  binary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
binary_summary_X_and_confint <-
  binary_summary_X_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_X_and <- binary_summary_X_and %>% full_join(binary_summary_X_and_confint, by="est") %>% unique()

binary_summary_XY_or <-
  binary_summary %>%
  filter(card_type=="XY", guess_type=="XorY")
binary_summary_XY_or_confint <-
  binary_summary_XY_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_XY_or <- binary_summary_XY_or %>% full_join(binary_summary_XY_or_confint, by="est") %>% unique()

binary_summary_X_or <-
  binary_summary %>%
  filter(card_type=="X", guess_type=="XorY")
binary_summary_X_or_confint <-
  binary_summary_X_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
binary_summary_X_or <- binary_summary_X_or %>% full_join(binary_summary_X_or_confint, by="est") %>% unique()

binary_summary <- bind_rows(binary_summary_X_cat, binary_summary_XY_cat, binary_summary_XY_ele, binary_summary_X_ele,
                                binary_summary_XY_and, binary_summary_X_and, binary_summary_XY_or, binary_summary_X_or)

binary_summary$response <- factor(binary_summary$response, levels = c("Wrong","Right"))
binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
binary_summary <- binary_summary %>% rename(proportion = "est")
```

```{r binaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}
binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=12)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE) +
  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))

@@

```{r ternaryData}
ternary_summary<-
  data %>%
  filter(response_type=="ternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), est=count/total)

ternary_summary_X_cat <-
  ternary_summary %>%
  filter(card_type=="X", guess_type=="X")
ternary_summary_X_cat_confint <-
  ternary_summary_X_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_X_cat <- ternary_summary_X_cat %>% full_join(ternary_summary_X_cat_confint, by="est")

ternary_summary_XY_cat <-
  ternary_summary %>%
  filter(card_type=="XY", guess_type=="X")
ternary_summary_XY_cat_confint <-
  ternary_summary_XY_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_XY_cat <- ternary_summary_XY_cat %>% full_join(ternary_summary_XY_cat_confint, by="est")

ternary_summary_XY_ele <-
  ternary_summary %>%
  filter(card_type=="XY", guess_type=="Z")
ternary_summary_XY_ele_confint <-
  ternary_summary_XY_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_XY_ele <- ternary_summary_XY_ele %>% full_join(ternary_summary_XY_ele_confint, by="est") %>% unique()

ternary_summary_X_ele <-
  ternary_summary %>%
  filter(card_type=="X", guess_type=="Z")
ternary_summary_X_ele_confint <-
  ternary_summary_X_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_X_ele <- ternary_summary_X_ele %>% full_join(ternary_summary_X_ele_confint, by="est") %>% unique()

ternary_summary_XY_and <-
  ternary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
ternary_summary_XY_and_confint <-
  ternary_summary_XY_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_XY_and <- ternary_summary_XY_and %>% full_join(ternary_summary_XY_and_confint, by="est") %>% unique()

ternary_summary_X_and <-
  ternary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
ternary_summary_X_and_confint <-
  ternary_summary_X_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_X_and <- ternary_summary_X_and %>% full_join(ternary_summary_X_and_confint, by="est") %>% unique()

ternary_summary_XY_or <-
  ternary_summary %>%
  filter(card_type=="XY", guess_type=="XorY")
ternary_summary_XY_or_confint <-
  ternary_summary_XY_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_XY_or <- ternary_summary_XY_or %>% full_join(ternary_summary_XY_or_confint, by="est") %>% unique()

ternary_summary_X_or <-
  ternary_summary %>%
  filter(card_type=="X", guess_type=="XorY")
ternary_summary_X_or_confint <-
  ternary_summary_X_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
ternary_summary_X_or <- ternary_summary_X_or %>% full_join(ternary_summary_X_or_confint, by="est") %>% unique()

ternary_summary <- bind_rows(ternary_summary_X_cat, ternary_summary_XY_cat, ternary_summary_XY_ele, ternary_summary_X_ele,
                                ternary_summary_XY_and, ternary_summary_X_and, ternary_summary_XY_or, ternary_summary_X_or)

ternary_summary$response <- factor(ternary_summary$response, levels = c("Wrong","Neither", "Right"))
ternary_summary$guess_type <- factor(ternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
ternary_summary$guess_type <- recode(ternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
ternary_summary <- ternary_summary %>% rename(proportion = "est")
```

```{r ternaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}
ternary_plot<-
  ternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE) +
  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))

@@

```{r quaternaryData}
quaternary_summary<-
  data %>%
  filter(response_type=="quaternary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), est=count/total)

quaternary_summary_X_cat <-
  quaternary_summary %>%
  filter(card_type=="X", guess_type=="X")
quaternary_summary_X_cat_confint <-
  quaternary_summary_X_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_X_cat <- quaternary_summary_X_cat %>% full_join(quaternary_summary_X_cat_confint, by="est")

quaternary_summary_XY_cat <-
  quaternary_summary %>%
  filter(card_type=="XY", guess_type=="X")
quaternary_summary_XY_cat_confint <-
  quaternary_summary_XY_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_XY_cat <- quaternary_summary_XY_cat %>% full_join(quaternary_summary_XY_cat_confint, by="est")

quaternary_summary_XY_ele <-
  quaternary_summary %>%
  filter(card_type=="XY", guess_type=="Z")
quaternary_summary_XY_ele_confint <-
  quaternary_summary_XY_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_XY_ele <- quaternary_summary_XY_ele %>% full_join(quaternary_summary_XY_ele_confint, by="est") %>% unique()

quaternary_summary_X_ele <-
  quaternary_summary %>%
  filter(card_type=="X", guess_type=="Z")
quaternary_summary_X_ele_confint <-
  quaternary_summary_X_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_X_ele <- quaternary_summary_X_ele %>% full_join(quaternary_summary_X_ele_confint, by="est") %>% unique()

quaternary_summary_XY_and <-
  quaternary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
quaternary_summary_XY_and_confint <-
  quaternary_summary_XY_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_XY_and <- quaternary_summary_XY_and %>% full_join(quaternary_summary_XY_and_confint, by="est") %>% unique()

quaternary_summary_X_and <-
  quaternary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
quaternary_summary_X_and_confint <-
  quaternary_summary_X_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_X_and <- quaternary_summary_X_and %>% full_join(quaternary_summary_X_and_confint, by="est") %>% unique()

quaternary_summary_XY_or <-
  quaternary_summary %>%
  filter(card_type=="XY", guess_type=="XorY")
quaternary_summary_XY_or_confint <-
  quaternary_summary_XY_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_XY_or <- quaternary_summary_XY_or %>% full_join(quaternary_summary_XY_or_confint, by="est") %>% unique()

quaternary_summary_X_or <-
  quaternary_summary %>%
  filter(card_type=="X", guess_type=="XorY")
quaternary_summary_X_or_confint <-
  quaternary_summary_X_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quaternary_summary_X_or <- quaternary_summary_X_or %>% full_join(quaternary_summary_X_or_confint, by="est") %>% unique()

quaternary_summary <- bind_rows(quaternary_summary_X_cat, quaternary_summary_XY_cat, quaternary_summary_XY_ele, quaternary_summary_X_ele,
                                quaternary_summary_XY_and, quaternary_summary_X_and, quaternary_summary_XY_or, quaternary_summary_X_or)

quaternary_summary$response <- factor(quaternary_summary$response, levels = c("Wrong","Kinda Wrong", "Kinda Right", "Right"))
quaternary_summary$guess_type <- factor(quaternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quaternary_summary$guess_type <- recode(quaternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
quaternary_summary <- quaternary_summary %>% rename(proportion = "est")
```

```{r quaternaryPlot, fig.height=4, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}
quaternary_plot<-
  quaternary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE) + 
  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))

@@

```{r quinaryData}
quinary_summary<-
  data %>%
  filter(response_type=="quinary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), est=count/total)

quinary_summary_X_cat <-
  quinary_summary %>%
  filter(card_type=="X", guess_type=="X")
quinary_summary_X_cat_confint <-
  quinary_summary_X_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_X_cat <- quinary_summary_X_cat %>% full_join(quinary_summary_X_cat_confint, by="est")

quinary_summary_XY_cat <-
  quinary_summary %>%
  filter(card_type=="XY", guess_type=="X")
quinary_summary_XY_cat_confint <-
  quinary_summary_XY_cat$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_XY_cat <- quinary_summary_XY_cat %>% full_join(quinary_summary_XY_cat_confint, by="est")

quinary_summary_XY_ele <-
  quinary_summary %>%
  filter(card_type=="XY", guess_type=="Z")
quinary_summary_XY_ele_confint <-
  quinary_summary_XY_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_XY_ele <- quinary_summary_XY_ele %>% full_join(quinary_summary_XY_ele_confint, by="est") %>% unique()

quinary_summary_X_ele <-
  quinary_summary %>%
  filter(card_type=="X", guess_type=="Z")
quinary_summary_X_ele_confint <-
  quinary_summary_X_ele$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_X_ele <- quinary_summary_X_ele %>% full_join(quinary_summary_X_ele_confint, by="est") %>% unique()

quinary_summary_XY_and <-
  quinary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
quinary_summary_XY_and_confint <-
  quinary_summary_XY_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_XY_and <- quinary_summary_XY_and %>% full_join(quinary_summary_XY_and_confint, by="est") %>% unique()

quinary_summary_X_and <-
  quinary_summary %>%
  filter(card_type=="X", guess_type=="XandY")
quinary_summary_X_and_confint <-
  quinary_summary_X_and$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_X_and <- quinary_summary_X_and %>% full_join(quinary_summary_X_and_confint, by="est") %>% unique()

quinary_summary_XY_or <-
  quinary_summary %>%
  filter(card_type=="XY", guess_type=="XorY")
quinary_summary_XY_or_confint <-
  quinary_summary_XY_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_XY_or <- quinary_summary_XY_or %>% full_join(quinary_summary_XY_or_confint, by="est") %>% unique()

quinary_summary_X_or <-
  quinary_summary %>%
  filter(card_type=="X", guess_type=="XorY")
quinary_summary_X_or_confint <-
  quinary_summary_X_or$count %>%
  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
quinary_summary_X_or <- quinary_summary_X_or %>% full_join(quinary_summary_X_or_confint, by="est") %>% unique()

quinary_summary <- bind_rows(quinary_summary_X_cat, quinary_summary_XY_cat, quinary_summary_XY_ele, quinary_summary_X_ele,
                                quinary_summary_XY_and, quinary_summary_X_and, quinary_summary_XY_or, quinary_summary_X_or)

quinary_summary$response <- factor(quinary_summary$response, levels = c("Wrong","Kinda Wrong", "Neither", "Kinda Right", "Right"))
quinary_summary$guess_type <- factor(quinary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
quinary_summary$guess_type <- recode(quinary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
quinary_summary <- quinary_summary %>% rename(proportion = "est")
```

```{r quinaryPlot, fig.height=4, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}
quinary_plot<-
  quinary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE) +
  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))

@@

## Analysis

```{r implicatureResultss}
implicature_results<-
  implicature_rate %>%
  group_by(response_type, trial_type, implicature, definition) %>%
  summarize(counts = n()) %>%
  group_by(response_type, trial_type, definition) %>%
  mutate(total = sum(counts), proportion = counts/total)

implicature_plot <- 
  implicature_results %>% filter(implicature==1)

binomial_confint<- binom.confint(implicature_plot$counts, implicature_plot$total, method="logit") %>%
  rename(counts = "x", total="n")

implicature_results <- implicature_plot %>% full_join(binomial_confint, by=c("total", "counts")) %>% unique

implicature_results$response_type <- fct_relevel(implicature_results$response_type, "binary", "ternary", "quaternary", "quinary")
implicature_results$implicature <- as.factor(implicature_results$implicature)
```

@@

We considered two linking assumptions. First we defined a weak (lenient) linking assumption in which any response lower than the maximum point on the scale (i.e. "right") is considered evidence for implicature computation. Second, we defined a strong (strict) linking assumption that only considered the lowest point on the scale (i.e. "wrong") as evidence for implicature computation. For each condition in our study (binary, ternary, quaternary, and quinary) and each implicature trial type (exhaustive and scalar), we computed a weak and a strong implicature rate. Figure \@ref(fig:implicatureRatePlot) shows these computed rates.

Comparing the strong and weak rows on Figure \@ref(fig:implicatureRatePlot), we see that a weak linking assumption tends to estimate higher implicature rates, especially in tasks with more response options. With a strong linking assumption, the binary and possibly ternary judgment tasks derive higher implicature rates than quaternary and quinary tasks. With a weak linking assumption, the pattern is reversed. Quaternary and quinary tasks estimate higher rates than binary and ternary tasks. The patterns show that estimates of "implicature rate" depend on linking assumptions and the number of responses available to participants in the study.

Comparing the exhaustive and scalar columns of Figure \@ref(fig:implicatureRatePlot), we see that with a strong linking assumption, there are slightly higher rates for scalar implicatures in the binary and ternary tasks. With a weak linking assumption, there may be slightly higher rates for scalar implicatures in the binary and ternary while the rates may be lower in the quaternary and quinary tasks. In what follows, we test the effect of linking assumption and response options on exhaustive and scalar implicature rates more formally.
